Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-10-26 ms.tex
switched to showing the median PSFs instead of just example images.
added in a note about the int times for the 5 subarray OTIS tests.

\begin{figure*}
\gridline{\fig{wlp8_otis_psf.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{grism_otis_psf.pdf}{0.99\textwidth}{Grism Image}}
\caption{Example OTIS  images obtained simultaneously during the long duration time series.
Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
}\label{fig:otisPSFs}
\end{figure*}

@@

>>>>

\begin{figure*}
\gridline{\fig{wlp8_otis_psf.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{grism_otis_psf.pdf}{0.99\textwidth}{Grism Image}}
\caption{Median images of the short wavelength (SW) and long wavelength (LW) that were used simultaneously in a grism stability long time series.
Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
}\label{fig:otisPSFs}
\end{figure*}

@@

Note that the integration times are different for these 4 tests. They are 39.9, 39.9, 32.3, 31.8 and 32.2 for the 64-STRIPE, 128-STRIPE, 256-STRIPE, 256-WIND and FULLFRAME respectively. Perhaps the lamp has oscillations on a timescale that are averaged out efficiently at 39.9 seconds but not 32.3 seconds?
